Monitoring Time Series With Missing Values:\\a Deep Probabilistic Approach

### 2022-03-15 paper.tex

More generally though, the epistemic noise is better modelled
heteroskedastically, and a two-parameter loss distribution,
with the location and the scale as the parameters.
In the case of the frequently used normal (Gaussian)
distribution, the output vector consists of means $\mu$
(location) and standard deviations $\sigma$ (scale) of all
dimensions and is twice as wide as the input.

>>>>

More generally though, the epistemic noise is better modelled
heteroskedastically, using a two-parameter loss distribution,
with the location and the scale as the parameters.
In the case of the frequently used normal (Gaussian)
distribution, the output vector consists of means $\mu$
(location) and standard deviations $\sigma$ (scale) of all
dimensions and is twice as wide as the input.
